latex
\documentclass[12pt, a4paper]{article}

% --- Настройка кодировок и шрифтов ---
\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{geometry}
\geometry{left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm}

% --- Гиперссылки ---
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}

% --- Заголовок ---
\title{\textbf{THE APh DOCTRINE} \\ \large SET-THEORETIC MODEL OF REALITY}
\author{Oleg Kurbanov}
\date{}

\begin{document}

\maketitle
\begin{center}
    \small
    Contact: \href{mailto:doctrine_xxi@icloud.com}{doctrine\_xxi@icloud.com} \\
    ORCID: \href{https://orcid.org}{orcid.org/0009-0005-8542-4826} \\
    DOI: \href{https://doi.org}{doi.org/10.5281/zenodo.18735058}
\end{center}

\vspace{1.5em}

% --- ГЛАВНАЯ ФОРМУЛА ---
\begin{equation*}
\mathsf{OR} \implies \top ! \ |^{\mathsf{OR}} \ \big( \ B \ \land \ \nabla(B) \ \big) \ \downarrow \ \mathsf{Ax_{OBJ}} \ |^\mathsf{OR} \ \vdash \ \mathfrak{S}^{* \circlearrowleft} \ \langle \ B_1 \ \dots \ B_n \ ; \ \Sigma \ \rangle \twoheadrightarrow \mathfrak{AR} \equiv \langle \mathfrak{A}, \mathfrak{R}; \Sigma \rangle
\end{equation*}

\vspace{1.5em}

\begin{abstract}
The APh Doctrine definitively establishes a formal framework for the interpretation of reality through a closed-loop architectural model. By utilizing set-theoretic formalism and the principle of generative closure ($\mathfrak{S}^{* \circlearrowleft}$), it defines the limit of cognition and the synthesis of derivative realities.
\end{abstract}

\section{Genesis and Interpretation}
\begin{itemize}
    \item \textbf{Genesis:} A finite system of absolute, categorical propositions.
    \item \textbf{Interpretation:} The derivation of the "Architecture of the Universe" based on the Genesis. The inherent uncertainty of the Genesis--Interpretation relation is reduced to a specific \textit{Signature} ($\Sigma$), which is indicated but remains undefined.
    \item \textbf{Plurality:} The doctrine postulates a singular Genesis corresponding to an infinite manifold of Interpretations.
\end{itemize}

\section{Ontological Basis}
A finite, closed system of fundamental categories acting as a "firewall" between the Unknowable and the Knowable (\textit{The Limit of Cognition}). 
\begin{itemize}
    \item \textbf{Set-Theoretic Formalism:} Basal categories are treated as primary, atomic sets (logical units) that are orthogonal and non-derivable, constituting the "Alphabet of the Universe."
    \item \textbf{Generative Closure ($\mathfrak{S}^{* \circlearrowleft}$):} The Basis generates all possible models through its signature, while ensuring that no derived element can transcend the boundaries of the initial set.
\end{itemize}

\section{Principal Implications}

\textbf{Mathematics:} Formal substantiation of fundamental uncertainty. Re-evaluation of the \textit{Axiom of Choice} and \textit{Gödelian Incompleteness} within the APh-closed framework.

\vspace{0.5em}
\textbf{Physics:} Theoretical physics as an operation with "phantom reality." Time is identified as lacking independent physical existence. Proof of the fundamental impossibility of a \textit{Grand Unified Theory} (GUT).

\vspace{0.5em}
\textbf{Economics \& Social Governance:} Establishment of the \textit{Money--Time Identity}. Refutation of classical Property theories (Smith, Marx, Coase) in favor of the \textit{Property--Object of Law} identity.

\vspace{0.5em}
\textbf{AI \& UIS:} Deployment of a new APh-based engine for AI, creating a radical leap in data processing power via the \textit{Universal Information System} (UIS).

\vspace{3em}
\begin{center}
    \rule{0.5\textwidth}{0.4pt} \\
    \textit{The APh Doctrine --- A Final Framework for Universal Architecture.}
\end{center}

\end{document}
